---
output: html_document
---

```{r setup, include=FALSE,message=FALSE,warning=F}
knitr::opts_chunk$set(echo = F)
library(dplyr);library(lubridate);library(readr);library(highcharter);library(ggplot2)
load("limits_report.Rdata")
```

Good `r ifelse(am(Sys.time()),"morning","afternoon")`,

Please find attached Loan limits and multiple loans analysis.

### Insights

#### Loan Limits
```{r}
abovelimns = reports$limits_check
duplicates_mobile = reports$duplicates_summary$mobile
duplicates_accid = reports$duplicates_summary$accountid
duplicates_idnumber = reports$duplicates_summary$idnumber
total_duplicates = sum(nrow(duplicates_mobile),nrow(duplicates_accid),nrow(duplicates_idnumber))
```

There were `r ifelse(nrow(abovelimns)>0,nrow(abovelimns),0)` disbursments records above limit on `r Sys.Date()-1`

#### Duplicates

There were `r ifelse(total_duplicates > 0,total_duplicates,'no')` duplicated disbursement records by National IDs,Phone Numbers or Account IDs.Details in the attachment.

#### Disbursements

Below is a summary of current month and previous day disbursement report respectively.

##### Cumulative Disbursement as at `r Sys.Date()-1`

```{r month disbursement,fig.align="center", echo = FALSE,fig.width = 10,fig.height = 5}
reports$disb_summ$month_disb %>% 
    filter(!grepl('Total',Channel)) %>%
    mutate(Amount=parse_number(Amount)) %>% 
    ggplot(aes(reorder(Product,Amount),Amount))+
    geom_col(fill='purple')+
    facet_wrap(Channel ~ .,scales = 'free') +
    labs(x = "Product",y="Amount(In Millions)")+
    theme(axis.text.x  = element_text(angle=45,vjust = .5,hjust = .5)) +
    scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
    geom_text(
        aes(label = ifelse(Amount >0,paste(format(round(Amount/1000000,2), big.mark = ","),"M"),Amount)),
        position = position_dodge(width = 0.5),
        hjust = .5,vjust = -0.5,colour = "black",size = 2
  )
```

##### Day Disbursement for `r Sys.Date()-1`

```{r day disb ,fig.align="center", echo = FALSE,fig.width = 10,fig.height = 5}
reports$disb_summ$day_disb %>% 
    filter(!grepl('Total',Channel)) %>%
    mutate(Amount=parse_number(Amount)) %>% 
    ggplot(aes(reorder(Product,Amount),Amount))+
    geom_col(fill='purple')+
    facet_wrap(Channel ~ .,scales = 'free') +
    labs(x = "Product",y="Amount(In Millions)")+
    theme(axis.text.x  = element_text(angle=45,vjust = .5,hjust = .5)) +
    scale_y_continuous(labels = scales::unit_format(unit = "M", scale = 1e-6))+
    geom_text(
        aes(label = ifelse(Amount >0,paste(format(round(Amount/1000000,2), big.mark = ","),"M"),Amount)),
        position = position_dodge(width = 0.5),
        hjust = .5,vjust = -0.5,colour = "black",size = 2
  )
```


Kind regards,

[!Signature](/temp/signature.jpg)

```{r}

# mbanalytics::maisha_email_push2(
#     to = "george.oduor@maishabank.com",
#     Recipient = "",Subject = "TEST",
#     from = "george.oduor@maishabank.com",
#     message = paste0(readLines("email2.html"),collapse = ""),
#     Sender = "George",test = F,
#     credfile = "E:/Automation/resources/george")

```




